Staged Abstract Interpreter

### 2018-01-05 paper.tex
outline
update outline

Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

2. From a performance perspective, closure is still not an efficient enough representation.

We implement staged abstract interpreter in a big-step semantics (abstract definitional interpreter) 
using Scala with LMS framework.  
Show it generates sound and high-performance low-level analysis code with 
various precisions and sensitivities, for instances, k-CFA, pushdown or m-CFA.

@@

3. Modular analysis for free?

Motivation: one of the challenges of modern static analysis is program usually depends on
large libraries programs\cite{toman_et_al:LIPIcs:2017:7121}. 
Can we analyze programs and libraries separately without losing precision? So that we can 
reduce part of the overhead of repeatedly analyzing libraries for different programs.
Similarly, some static analyzers compute summary for a function or a module, that can be reused
later(Facebook Infer). But to my knowledge, they are mostly context-insensitive or imprecise.

@@

4. Show the evaluation result on benchmark programs.

@@

\textbf{Abstract Compilation}. The idea in this paper was closely inspired by 
abstract compilation \cite{Boucher:1996:ACN:647473.727587}.
\citeauthor{Boucher:1996:ACN:647473.727587} presented abstract compilation
techniques as an efficient implementation of the monovariant flow analysis 
\textit{0}-CFA for programs in continuation-passing style. The key idea is to 
reduce the interpretation overhead on traversing the syntax tree by partial evaluation.
Specifically, they proposed two kinds of abstract compilers to achieve this. 
The first one is to generate specialized analysis as a textual program, then 
can be loaded and executed by \texttt{eval} or similar mechanisms. The second 
one is using closure as a representation of specialized analysis. 
A closure is a function that remembers the environment where it defined. So the 
abstract compiler generates higer-order functions on-the-fly rather than textual 
program, then the functions can be applied immediately in a higher-order host language.

>>>>

2. Generalize the idea to staged abstract interpreter.
We implement staged abstract interpreter within a big-step abstract semantics 
(abstract definitional interpreter) using Scala with LMS framework.  
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

3. Improve performance (closure is still not an efficient enough representation).

Show it generates sound and high-performance low-level analysis code with 
various precisions and sensitivities, for instances, k-CFA, pushdown or m-CFA.

@@

4. Modular analysis for free?

Motivation: one of the challenges of modern static analysis is program usually depends on
large libraries programs\cite{toman_et_al:LIPIcs:2017:7121}. 
Can we analyze programs and libraries separately without losing precision? So that we can 
reduce part of the overhead of repeatedly analyzing libraries for different programs.
Similarly, some static analyzers compute summary for a function or a module, that can be reused
later (like Facebook Infer). But to my knowledge, they are mostly context-insensitive or imprecise.

@@

5. Show the evaluation result on benchmark programs (TODO: collect benchmark programs). 
Compare with normal abstract interpreter, 
abstract compilation\cite{Boucher:1996:ACN:647473.727587}, and OAAM \cite{Johnson:2013:OAA:2500365.2500604}.

@@

\textbf{Abstract Compilation}. The idea in this paper is closely inspired by 
abstract compilation \cite{Boucher:1996:ACN:647473.727587}.
\citeauthor{Boucher:1996:ACN:647473.727587} presented abstract compilation
techniques as an efficient implementation of the monovariant flow analysis 
\textit{0}-CFA for programs in continuation-passing style. The key idea is to 
reduce the interpretation overhead on traversing the syntax tree by partial evaluation.
Specifically, they proposed two kinds of abstract compilers to achieve this. 
The first one is to generate specialized analysis as a textual program, then 
can be loaded and executed by \texttt{eval} or similar mechanisms. The second 
one is using closure as a representation of specialized analysis. 
A closure is a function that remembers the environment where it defined. So the 
abstract compiler generates higer-order functions on-the-fly rather than textual 
program, then the functions can be applied immediately in a higher-order host language.
